Network Data Collection for Artifical Intelligence

### 2020-02-25 paper2/paper2.tex
Modify expressions and cites

GNS3 (Graphical Network Simulator 3) is a very popular free open source software to emulate and test networks. It offers the integration of virtual machines and real networks and supports models of various vendors but does not offer pre-installed device images due to license issues. It also provides a RESTful API to setup network topologies, a big community and scalability. The software can be easily installed through packages on all operating systems and supports all hypervisors as well Docker containers. Performance tests showed a long topology loading time with high CPU load but a good response through the user interface. Fig.~\ref{gns3} shows a sample network topology created with GNS3.  \cite{b1} \cite{b5}

@@

Regarding these factors GNS3 fullfills our requirements the most because it is free, supports all vendors and comes with a big community and documentation. Our second option would be EVE-NG in the professional edition which also supports all vendors.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.25]{docker_vm.png}}
\caption{Virtual machines vs. Containers \cite{b8}}
\label{docker-vm}
\end{figure}

Hypervisors like VirtualBox or VMware provide the possibility to setup full virtual computers on a physical host where Docker containers are encapsuled sandboxes on an existing operating system like illustrated in Fig.~\ref{docker-vm}. It is clear that containers are more resource efficent but in virtual machines the systems are better isolated. In our case we could use both solutions because the network simulators are also capable to run in Docker containers. If we focus on resource efficency and scalability also Kubernetes comes in our minds which is an orchestrator for deploying Docker containers on multiple nodes but it is a more complex configuration overhead and needs certain amount of hardware to unfold its potential also for simple scenarios. Because we want an affordable solutions which can be used in most of the cases also on our computers with some exceptions, we decided to use a tool which can create virtual machines as well as Docker containers to be ready for the future. Regarding the corner cases servers or a Kubernetes cluster could be rented temporarily on cloud platforms to support high-load scenarios e.g. big denial-of-service attacks.

A popular solution to bootstrap development environments in virtual machines is called Vagrant which provides lightweight base images and an interface to automate the configuration of the virtual machines. Moreover it can be connected to provisioning tools to further configure host systems. Vagrant supports VirtualBox or VMware but also Docker and can be extended to support cloud services like AWS or even to install a whole Kubernetes cluster. It gives us the power to start with simple configurations and scale them up to more sophisticated ones using containerization and complex orchestrators. \cite{b9}

This means we are ready to create system environments on our host or in the cloud and install base systems on them. The next section focuses on the automated setup of the network simulator, recorder and data extractor within virtual machines or Docker containers as well as the configuration of network topologies based on the selected scenarios and parameters to produce, record and extract network traffic for further processing in neuronal networks to improve their strike rate.

@@

Vagrant supports multiple provisioners like Ansible, Terraform or simple bash scripts to configure the host systems and can also be set up through them. For the beginning we will use Ansible through Vagrant to configure the host system. Vagrant can setup multiple virtual machines or Docker containers on one host. If we would need to set up machines on multiple hosts we will come back to tools like Terraform for example. \cite{b9}

If all the possible network scenarios are defined these network topologies have to be deployed through our deployment system consisting of Vagrant and Ansible. This means we will define the basic host setup and the network configurations for all the scenarios in Ansible templates which could be later adjusted via command line parameters. The topology can then be deployed by executing a shell command. This includes the deployment of the network recorder and the data extractor. In other words one or multiple scenarios can be started and connected to one recorder and data extractor to combine simultaneous attacks and everything will be deployed through a shell command with static configuration in templates and dynamic configuration with command line options. It will be also possible to integrate real hardware into the simulation.

@@

Fig.~\ref{docker-vm} shows a schematic overview of the simulation workflow. The input parameters are the type of scenario(s) and the respective settings which deploys hosts including the base systems and the simulators applying the network topologies. Moreover the network recorder and data extractor will be deployed to gather the network traffic and extract the features to create data sets which could be collected in a central database.

@@

\subsection*{Label definition}

@@

@@

\bibitem{b1} CBT Nuggets Blog (2020). 5 Best Network Simulators for Cisco Exams: CCNA, CCNP, CCIE. [online] Available at: \newline\url{https://www.cbtnuggets.com/blog/career/career-progression/5-best-network-simulators-for-cisco-exams-ccna-ccnp-and-ccie} [Accessed 22 Feb. 2020].

@@

\bibitem{b8} SOSC-2018. (2020). Docker. [online] Available at: \url{https://dodas-ts.github.io/SOSC-2018/docker.html} [Accessed 22 Feb. 2020].
\bibitem{b9} Chan, M. (2020). 15 Infrastructure as Code Tools to Automate Deployments - Thorn Tech. [online] Thorn Technologies. Available at: \url{https://www.thorntech.com/2018/04/15-infrastructure-as-code-tools/} [Accessed 22 Feb. 2020].

@@

>>>>

GNS3 (Graphical Network Simulator 3) is a very popular free open source software to emulate and test networks. It offers the integration of virtual machines and real networks and supports models of various vendors but does not offer pre-installed device images due to license issues. It also provides a RESTful API to set up network topologies, a big community and scalability. The software can be easily installed through packages on all operating systems and supports all hypervisors as well Docker containers. Performance tests showed a long topology loading time with high CPU load but a good response through the user interface. Fig.~\ref{gns3} shows a sample network topology created with GNS3.  \cite{b1} \cite{b5}

@@

Regarding these factors GNS3 fullfills our requirements the most because it is free, supports all vendors and comes with a big community and documentation. Our second option could be EVE-NG in the professional edition which also supports all vendors.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[scale=0.5]{docker_vm.png}}
\caption{Virtual machines vs. Containers \cite{b8}}
\label{docker-vm}
\end{figure}

Hypervisors like VirtualBox or VMware provide the possibility to set up full virtual computers on a physical host where Docker containers are encapsuled sandboxes on an existing operating system like illustrated in Fig.~\ref{docker-vm}. It is clear that containers are more resource efficent but in virtual machines the systems are better isolated. In our case we could use both solutions because the network simulators are also capable to run in Docker containers. If we focus on resource efficency and scalability also Kubernetes comes in our minds which is an orchestrator for deploying Docker containers on multiple nodes but it is a more complex configuration overhead and needs certain amount of hardware to unfold its potential also for simple scenarios. Because we want an affordable solutions which can be used in most of the cases also on our computers with some exceptions, we could use a tool which can create virtual machines as well as Docker containers to be ready for the future. Regarding the corner cases servers or a Kubernetes cluster could be rented temporarily on cloud platforms like AWS to support high-load scenarios e.g. big denial-of-service attacks. \cite{b8}

A popular solution to bootstrap development environments in virtual machines is called Vagrant which provides lightweight base images and an interface to automate the configuration of the virtual machines. Moreover it can be connected to provisioning tools to further configure host systems. Vagrant supports VirtualBox or VMware but also Docker and can be extended to support cloud services like AWS or even to install a whole Kubernetes cluster. It gives us the power to start with simple configurations and scale them up to more sophisticated ones using containerization and complex orchestrators. \cite{b9} \cite{b10}

This means we would be ready to create system environments on our host or in the cloud and install base systems on them. The next section focuses on the automated setup of the network simulator, recorder and data extractor within virtual machines or Docker containers as well as the configuration of network topologies based on the selected scenarios and parameters to produce, record and extract network traffic for further processing in neuronal networks to improve their strike rate.

@@

Vagrant supports multiple provisioners like Ansible, Terraform or simple bash scripts to configure the host systems and can also be set up through them. For the beginning we could use Ansible through Vagrant to configure the host system. Vagrant can set up multiple virtual machines or Docker containers on one host. If we would need to set up machines on multiple hosts we could come back to tools like Terraform for example. \cite{b9} \cite{b10} \cite{b11}

If all the possible network scenarios are defined these network topologies have to be deployed through our deployment system. This means we could define the basic host setup and the network configurations for all the scenarios in Ansible templates which could be later adjusted via command line parameters. The topology can then be deployed by executing a shell command. This includes the deployment of the network recorder and the data extractor. In other words one or multiple scenarios can be started and connected to one recorder and data extractor to combine simultaneous attacks and everything will be deployed through a shell command with static configuration in templates and dynamic configuration with command line options. It will be also possible to integrate real hardware into the simulation. \cite{b9}

@@

Fig.~\ref{docker-vm} shows a possible simulation workflow. The input parameters are the type of scenario(s) and the respective settings which deploys hosts including the base systems and the simulators applying the network topologies. Moreover the network recorder and data extractor could be deployed to gather the network traffic and extract the features to create data sets which could be collected in a central database.

@@

A different approach is the use of features derived from raw system call traces. The advantage of system call traces over log files is that they contain only raw information about the interaction between programs and the operating system kernel, whereas log files contain data interpreted by various programs, and potentially include large amounts of irrelevant data. There are multiple methods of analysing system calls. Some only look at the pattern of system calls, while others also look at the arguments passed to these system calls. Also, there is a distinction between syntactic features, which depend only on contiguous patterns of system calls, and semantic features, which additionally consider the meaning of system call arguments or groups of discontiguous system calls. The advantage of the semantic approach is that it is able to counter mimicry attacks, where the payload is modified by the attacker with the aim that the system calls it executes cannot be classified as being malicious \cite{creech2014}.

\subsection{Label definition}

@@

\section{Conclusion}

The quality of a dataset is generally crucial for the performance of machine learning algorithms, and generating a high quality dataset for intrusion detection systems is not a simple task. While the generation of representative benign and malicious data in itself is fundamental, the goal of this paper was to give an overview about the equally important tasks of network simulation, recording and data extraction. For each of these tasks, a variety of different approaches has been examined. Because each approach has its own strengths and limitations, they have to be evaluated individually for each application, depending on its specific requirements. Also, the further development of the Internet and the ongoing introduction of new attack techniques has to be considered, which may affect the suitability of current methods in the future and therefore cause the necessity to alter them or to develop new ones.

@@

\bibitem{b1} Seifert, C. and Reißmann, S. and Rieger, S. and Pape, C. Evaluation von VIRL, GNS3 und Mininet als Virtual Network Testbeds in der Hochschullehre. 11. DFN-Forum Kommunikationstechnologien. Bonn: Gesellschaft für Informatik e.V.., pp. 103-112.

@@

\bibitem{b8} Bernstein, D. Containers and Cloud: From LXC to Docker to Kubernetes, in IEEE Cloud Computing, vol. 1, no. 3, pp. 81-84, Sept. 2014.
\bibitem{b9} Nishant Kumar Singh, S. Thakur, H. Chaurasiya and H. Nagdev, Automated provisioning of application in IAAS cloud using Ansible configuration management, 1st International Conference on Next Generation Computing Technologies (NGCT), Dehradun, 2015, pp. 81-85.
\bibitem{b10} Spanaki, P. Cloud Computing: Security Issues and Establishing Virtual Cloud Environment via Vagrant to Secure Cloud Hosts, 2018, pp. 539-553
\bibitem{b11} Ivanova, D. and Borovska, P. and Zahov, S. Development of PaaS using AWS and Terraform for medical imaging analytics, AIP Conference Proceedings, 2018

@@

\bibitem{creech2014} Creech, G. and Hu, J. (2014). A semantic approach to host-based intrusion detection systems using contiguous and discontiguous system call patterns. IEEE Transactions on Computers, vol. 63, no. 4, pp. 807-819, April 2014.
